---
title: "Pollution Outsourcing and Democracy 2"
author: "Ella Henninger"
date: "2023-07-25"
output:
  word_document: default
  html_document: default
---

# Contents of the replication packet

This R-Markdown file replicates all analyses and figures included in the paper "What Makes Democracies Greener? The Role of Pollution Offshoring" by Tobias Böhmelt, Ella Henninger, and Thomas Bernauer.

## Data
 - **Outsourcing data**: Presberger and Bernauer (2023), https://www.sciencedirect.com/science/article/pii/S0959378023000031?via%3Dihub
 - **Pollution data**: Van Donkelaar et al. (2021), https://pubs.acs.org/doi/full/10.1021/acs.est.1c05309
 - **Main data**: Quality of Governance database (QoG), https://www.gu.se/en/quality-government/qog-data
 - **Economic data**: World Development Indicators (2023), https://databank.worldbank.org/source/world-development-indicators#
 - **Democracy data**: V-Dem (2023), https://www.v-dem.net/data/the-v-dem-dataset/


**The code is structured as follows**:

1. Set up

2. Preparatory steps
2.1 Load data
2.2 Create lagged and logged variables

3. Descriptives
3.1 Table summary statistics

4. Analyses
4.1 Models democracy and pollution outsourcing: Model group 1
4.2 Models pollution outsourcing and environmental performance: Model group 2
4.3 Plots model group 1
4.4 Plots model group 2

5. Quantities of interest
5.1 Marginal effects plots
5.2 Expected values: Model group 1 
5.3 Expected values & first differences: Model group 2

6. Robustness checks
6.1 Replacing DV with PM2.5
6.2 Replacing DV with carbon footprint
6.3 Different outsourcing variables
6.4 Alternative operationalization outsourcing
6.5 Alternative operationalization democracy
6.6 Additional controls
6.7 Drop high-income states
6.8 Alternative model specifications

**As a note**: You may be asked to update some packages, please press "yes" to make sure the file runs smoothly.


# Set up

```{r setup, include=FALSE}

## clean environment
rm(list = ls())

# Define which packages needed for analyses
p_needed <-
  c("knitr",
    "dplyr", 
    "psych",
    "stargazer",
    "ggplot2",
    "viridis",
    "haven",
    "MASS",
    "modelsummary",
    "WDI",
    "plm",
    "lmtest",
    "ggmap",
    "maps",
    "tidyr",
    "devtools",
    "data.table",
    "sjPlot",
    "interplot",
    "fastDummies",
    "texreg",
    "interflex",
    "reshape2",
    "marginaleffects",
    "ggExtra",
    "cowplot")

# Check which packages are already installed on your computer
packages <- rownames(installed.packages())

# Check which packages are not installed
p_to_install <- p_needed[!(p_needed %in% packages)]

if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_needed, require, character.only = TRUE)


# Set an option for the final document that can be produced from the .Rmd file.
knitr::opts_chunk$set(echo = TRUE)

## For replicability: session information 
session_info <- print(sessionInfo())

```



# Preparatory steps

## Load data

```{r load data}

#-------------------------------------------------------------------------------
# Data
#-------------------------------------------------------------------------------
data <- read_dta("data/QoG/qog_std_ts_jan23_stata14.dta")

#-------------------------------------------------------------------------------
# Filter data
#-------------------------------------------------------------------------------
data <- data[which(data$year >= 1989),]
data <- data[which(data$year <= 2022),]

#-------------------------------------------------------------------------------
# Data - GHG emissions
#-------------------------------------------------------------------------------
ghg <- read_dta("data/GHG Emissions.dta")
ghg$ccodealp <- ghg$countrycode
ghg <- ghg[,c(3,4,6)]


#-------------------------------------------------------------------------------
# Match
#-------------------------------------------------------------------------------
data <- left_join(data, ghg, by = c("ccodealp", "year"))

data_ghg <- data[,c("ccodealp",
                    "year",
                    "en_atm_ghgt_kt_ce",
                    "wdi_pop",
                    "wdi_co2")]

data_ghg$ghg_pc <- data_ghg$en_atm_ghgt_kt_ce * 1000 / data_ghg$wdi_pop
data_ghg$ghg_pc_mt <- data_ghg$ghg_pc * 1000

```

## Create lagged and logged variables 

```{r variable selection}

#-------------------------------------------------------------------------------
# Create GHG per capita
#-------------------------------------------------------------------------------
data$ghg_pc <- data$en_atm_ghgt_kt_ce * 1000 / data$wdi_pop # transform into metric tons
data$ghg <- data$en_atm_ghgt_kt_ce

summary(log(data$ghg_pc + 1))

#-------------------------------------------------------------------------------
# Create logs
#-------------------------------------------------------------------------------
data$insourced_GHG <- data$cf_cc_pop_mean
data$log_wdi_co2 <- log(1 + data$wdi_co2)  ## plus 1 to avoid negative numbers
data$log_ghg <- log(data$ghg)
data$log_ghg_pc <- log(data$ghg_pc + 1)

## outsourced CO2
data$log_cc_outs <- log(data$cf_cc_pop_mean_outs)
data$log_cc_sum_outs <- log(data$cf_cc_pop_sum_outs + 1)

## other outsourcing variabes
data$log_lu_outs <- log(data$cf_lu_pop_mean_outs + 1)
data$log_en_outs <- log(data$cf_en_pop_mean_outs)
data$log_mf_outs <- log(data$cf_mf_pop_mean_outs)
data$log_bw_outs <- log(data$cf_bw_pop_mean_outs)

## pm2.5
data$log_pm25_pop <- log(data$populationweightedpm25ugm3)
data$log_pm25_geo <- log(data$geographicmeanpm25ugm3)

## carbon footprint of consumption
data$log_ef_carb <- log(data$ef_carb)

## population
data$log_pop <- log(data$wdi_pop)
data$log_pop_den <- log(data$wdi_popden)

## gdp
data$log_gdp_pc <- log(data$wdi_gdpcapcon2015)
data$log_gdp_pc_sq <- data$log_gdp_pc^2
data$log_gdp <- log(data$wdi_gdppppcon2017)


#-------------------------------------------------------------------------------
# Create environmental treaties variable
#-------------------------------------------------------------------------------
data <- data %>% 
  group_by(ccode) %>% 
  mutate(env_treaties = ifelse(any(!is.na(iea_sum_i)), zoo::na.locf(iea_sum_i), NA))

data$env_treaties <- data$env_treaties/100

#-------------------------------------------------------------------------------
# Transform Freedom House civil liberties variable
#-------------------------------------------------------------------------------
data$fh_cl <- 8 - data$fh_cl

#-------------------------------------------------------------------------------
# Rescale political globalization variable (1-10)
#-------------------------------------------------------------------------------
data$dr_pg <- data$dr_pg/100

#-------------------------------------------------------------------------------
# Subset data to relevant variables
#-------------------------------------------------------------------------------
data_s <- dplyr::select(data, "cname", "ccode", "year", "ccodealp", 
                              "ghg", "ghg_pc", "log_ghg", "log_ghg_pc",
                              "insourced_GHG", "cf_cc_pop_mean", "cf_cc_pop_mean_outs", "cf_cc_pop_sum_outs", "log_cc_outs",
                              "log_cc_sum_outs",
                              "log_lu_outs", "log_mf_outs", "log_bw_outs", "log_en_outs",
                              "log_pm25_pop", "log_pm25_geo", "log_wdi_co2", "wdi_co2",
                              "populationweightedpm25ugm3", "geographicmeanpm25ugm3",
                              "ef_carb", "log_ef_carb",
                              "vdem_polyarchy", "log_gdp_pc", "log_gdp_pc_sq", "log_gdp",
                              "log_pop", "log_pop_den", "fh_cl", "fh_fog",
                              "cf_bw_pop_mean_outs", "cf_en_pop_mean_outs", "cf_lu_pop_mean_outs", "cf_mf_pop_mean_outs",
                              "dr_pg", "fh_status", "env_treaties",  "wdi_trade",
                              "p_polity2", "vdem_partip", "vdem_delibdem", "wdi_gdpind")

```



# Descriptives

## Table summary statistics

```{r descriptives}

#-------------------------------------------------------------------------------
# Table: Summary statistics
#-------------------------------------------------------------------------------
data_descript <- data_s[which(!is.na(data_s$log_cc_outs) &
                             # !is.na(data_s$log_ghg) &
                              data_s$log_ef_carb != -Inf),]

# options("modelsummary_format_numeric_latex" = "plain")
# datasummary(formula = (`Pollution Outsourcing` = cf_cc_pop_mean_outs) + (`ln(Pollution Outsourcing)` = log_cc_outs) +
#                       (`ln(GHG)` = log_ghg) +
#                       (`ln(CO2)` = log_wdi_co2) +
#                       (`ln(PM2.5) (pop. weighted)` = log_pm25_pop) +
#                       (`ln(Environm. Footprint Consumpt.)` = log_ef_carb) +
#                       (`Democracy` = vdem_polyarchy) + (`ln(GDP)` = log_gdp) +
#                       (`ln(GDP per capita)` = log_gdp_pc) + (`ln(Populat. Size)`= log_pop) +
#                       (`Civil liberties (Freedom House)` = fh_cl) +
#                       (`Democracy (Polity V)` = p_polity2) + (`Political Globaliz.` = dr_pg) +
#                       (`Trade Openness` = wdi_trade) + (`Environm. Treaties` = env_treaties)
#               ~ N + Mean + SD + Min + Median + Max,
#             title = "Summary statistics",
#             data = data_descript,
#             output = "latex")

```


# Analyses

## Model group 1

```{r within-between 1}

## Reduce to correct length
data_ova <- data_s[which(!is.na(data_s$log_cc_outs) &
                         !is.na(data_s$vdem_polyarchy) &
                         !is.na(data_s$log_pop) &
                         !is.na(data_s$log_gdp_pc) &
                         !is.na(data_s$log_wdi_co2)),]

#-------------------------------------------------------------------------------
# Model group 1
#-------------------------------------------------------------------------------
m1 <- lm(log_cc_outs ~ vdem_polyarchy + as.factor(year), data = data_ova)
m2 <- lm(log_cc_outs ~ log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), data = data_ova)
m3 <- lm(log_cc_outs ~ vdem_polyarchy + log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), data = data_ova)

stargazer(m1, m2, m3, type = "text", omit = "year")

texreg(list(m1, m2, m3),
       stars = c(0.01, 0.05, 0.1),
       #file = "texreg1.doc",
       custom.header = list("Pollution Outsourcing" = 1:3),
       caption = "Democracy and Pollution Outsourcing",
       label = "tab:table1",
       caption.above = T,
       fontsize = "scriptsize",
       custom.coef.map = list("vdem_polyarchy" = "Democracy",
                              "log_pop" = "Population",
                              "log_gdp_pc" = "GDP per capita",
                              "log_gdp_pc_sq" = "GDP per capita$^2$", 
                              "(Intercept)" = "Constant"),
        custom.gof.rows = list("Controls" = c("\\xmark", "\\ding{51}", "\\ding{51}"),
                               "Year-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}")))



```

## Plot coefficients: Model group 1

```{r plots coefficients 1}

#-------------------------------------------------------------------------------
# Coefficient plot 
#-------------------------------------------------------------------------------
coefs_m1 <- as.data.frame(summary(m3)$coefficients[c(2:5),])

# Create data frames for each model
coefs_m1$CI_low <- coefs_m1[,"Estimate"] - qnorm(0.95)*coefs_m1[,"Std. Error"]
coefs_m1$CI_high <- coefs_m1[,"Estimate"] + qnorm(0.95)*coefs_m1[,"Std. Error"]


pdf("Plots/Coefficients_table1.pdf", width = 7.5)

par(mar = c(5.1, 10, 2.5, 2.1)) # c(bottom, left, top, right))

plot(1,
     type = "n",
     ylim = c(0,2),
     bty = "n",
     xlab = "Coefficients and 95% confidence intervals",
     xlim = c(-1.75, 2.25),
     ylab = "",
     yaxt = "n",
     cex.lab = 1.1)


# add grid
segments(x0 = c(-1.25,-1,-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75, 1, 1.25, 1.5, 1.75, 2), y0 = 0,
         x1 = c(-1.25,-1,-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75, 1, 1.25, 1.5, 1.75, 2), y1 = 2,
         col = "lightgrey",
         lty = "solid", lwd = 0.7)

segments(x0 = -1.5, y0 = rev(c(0.25, 0.5, 0.75, 1,
                               1.25, 1.5, 1.75)),
         x1 = 2, y1 = rev(c(0.25, 0.5, 0.75, 1,
                               1.25, 1.5, 1.75)),
         col = "lightgrey",
         lty = "solid", lwd = 0.7)

# add null line
segments(x0 = 0, y0 = 0,
         x1 = 0, y1 = 2.5,
         lty = "solid", lwd = 1, col = "black")


# add point estimates
points(x = coefs_m1$Estimate,
       y = rev(c(0.25, 0.75, 1.25, 1.75)),
       pch = 16,
       col = c(viridis(3)[1], viridis(3)[1], viridis(3)[1], viridis(3)[1]),
       cex = 1)

# add CIs
segments(y0 = rev(c(0.25, 0.75, 1.25, 1.75)), 
         y1 = rev(c(0.25, 0.75, 1.25, 1.75)), 
         col = c(viridis(3)[1], viridis(3)[1], viridis(3)[1], viridis(3)[1]),
         x0 = coefs_m1$CI_low,
         x1 = coefs_m1$CI_high,
         lwd = 3, cex = 1.3, lend = 1)

# add coefficients text
text(x = -2.75,
     y = rev(c(0.25, 0.75, 1.25, 1.75)),
     labels = c("Democracy", "Population", "GDP per capita", expression("GDP per capita"^2)),
     xpd = T,
     cex = 0.9,
     pos = 4)

dev.off()

```

## Model group 2

```{r within-between 2}

#-------------------------------------------------------------------------------
# Model group 2 - R & R
#-------------------------------------------------------------------------------
m5 <- lm(log_ghg_pc ~ log_cc_outs + vdem_polyarchy + as.factor(year), data = data_ova)
m6 <- lm(log_ghg_pc ~ log_cc_outs + vdem_polyarchy + log_cc_outs*vdem_polyarchy + as.factor(year), data = data_ova)
m7 <- lm(log_ghg_pc ~ log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), data = data_ova)
m8 <- lm(log_ghg_pc ~ log_cc_outs + vdem_polyarchy + log_cc_outs*vdem_polyarchy +
           log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), data = data_ova)

stargazer(m5, m6, m7, m8, type = "text", omit = "year")

texreg(list(m5, m6, m7, m8),
       stars = c(0.01, 0.05, 0.1),
      # file = "texreg2.doc",
       custom.header = list("GHG emissions" = 1:4),
       caption = "Environmental Performance and Pollution Outsourcing",
       custom.model.names = c("Model 4", "Model 5", "Model 6", "Model 7"),
       label = "tab:table2",
       caption.above = T,
       fontsize = "scriptsize",
       custom.coef.map = list("log_cc_outs" = "Pollution Outsourcing",
                              "vdem_polyarchy" = "Democracy",
                              "log_cc_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "log_pop" = "Population",
                              "log_gdp_pc" = "GDP per capita",
                              "log_gdp_pc_sq" = "GDP per capita$^2$",
                              "(Intercept)" = "Constant"),
        custom.gof.rows = list("Controls" = c("\\xmark", "\\xmark", "\\ding{51}", "\\ding{51}"),
                               "Year-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}")))

```

## Plot coefficients: Model group 2

```{r plot coefficients 2}

#-------------------------------------------------------------------------------
# Coefficient plot - Model group 2
#-------------------------------------------------------------------------------
coefs_m2 <- as.data.frame(summary(m8)$coefficients[c(2,3,32,4:6),])

# Create data frames for each model
coefs_m2$CI_low <- coefs_m2[,"Estimate"] - qnorm(0.95)*coefs_m2[,"Std. Error"]
coefs_m2$CI_high <- coefs_m2[,"Estimate"] + qnorm(0.95)*coefs_m2[,"Std. Error"]


#-------------------------------------------------------------------------------
# Coefficient plot - Model group 2 - R & R
#-------------------------------------------------------------------------------
pdf("Plots/Coefficients_table2.pdf", width = 7.5)

par(mar = c(5.1, 10, 2.5, 2.1)) # c(bottom, left, top, right))

plot(1,
     type = "n",
     ylim = c(0,2.5),
     bty = "n",
     xlab = "Coefficients and 95% confidence intervals",
     xlim = c(-1.25, 1.5),
     ylab = "",
     yaxt = "n",
     cex.lab = 1.1)


# add grid
segments(x0 = c(-1.25,-1,-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75, 1, 1.25, 1.5, 1.75, 2), y0 = 0,
         x1 = c(-1.25,-1,-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75, 1, 1.25, 1.5, 1.75, 2), y1 = 2.5,
         col = "lightgrey",
         lty = "solid", lwd = 0.7)

segments(x0 = -1.5, y0 = rev(c(0.25, 0.45, 0.65, 0.85, 1.05, 1.25, 1.45, 1.65, 1.85, 2.05, 2.25)),
         x1 = 2, y1 = rev(c(0.25, 0.45, 0.65, 0.85, 1.05, 1.25, 1.45, 1.65, 1.85, 2.05, 2.25)),
         col = "lightgrey",
         lty = "solid", lwd = 0.7)

# add null line
segments(x0 = 0, y0 = 0,
         x1 = 0, y1 = 2.5,
         lty = "solid", lwd = 1, col = "black")


# add point estimates
points(x = coefs_m2$Estimate,
       y = rev(c(0.25, 0.65, 1.05, 1.45, 1.85, 2.25)),
       pch = 16,
       col = c(viridis(3, alpha = 0.6)[1], viridis(3)[1],viridis(3)[1],viridis(3)[1], viridis(3)[1],viridis(3, alpha = 0.6)[1]),
       cex = 1)

# add CIs
segments(y0 = rev(c(0.25, 0.65, 1.05, 1.45, 1.85, 2.25)), 
         y1 = rev(c(0.25, 0.65, 1.05, 1.45, 1.85, 2.25)), 
         col = c(viridis(3, alpha = 0.3)[1], viridis(3)[1], viridis(3)[1],viridis(3)[1], viridis(3)[1],viridis(3, alpha = 0.3)[1]),
         x0 = coefs_m2$CI_low,
         x1 = coefs_m2$CI_high,
         lwd = 3, cex = 1.3, lend = 1)

# add coefficients text
text(x = -2,
     y = rev(c(0.25, 0.65, 1.05, 1.35, 1.85, 2.25)),
     labels = c("Pollution outsourcing", "Democracy", "Pollution outsourcing \nx Democracy", 
                "Population", "GDP per capita", expression("GDP per capita"^2)),
     xpd = T,
     cex = 0.9,
     pos = 4)

dev.off()

```



# Quantities of interest

## Marginal effect plots

```{r marginal effects}

#-------------------------------------------------------------------------------
# Marginal effects 
#-------------------------------------------------------------------------------
# install.packages('devtools', repos = 'http://cran.us.r-project.org') # if not already installed
# devtools::install_github('xuyiqing/interflex')

#-------------------------------------------------------------------------------
# Preparation
ranef_m8 <- as.data.frame(coefficients(m8))
extract_year <- c(1990:2015)

## Reduce to correct length
data_ova <- data_s[which(!is.na(data_s$log_cc_outs) &
                         !is.na(data_s$vdem_polyarchy) &
                         !is.na(data_s$log_pop) &
                         !is.na(data_s$log_gdp_pc) &
                         !is.na(data_s$log_wdi_co2)),]

## Create dummy variables for countries and years
data_ova <- dummy_cols(data_ova[which(data_ova$year %in% extract_year),],
                       select_columns = c("year"))

data_ova <- as.data.frame(data_ova)

## Raw
out1_raw <- interflex(Y = "log_ghg_pc", 
                      D = "log_cc_outs", 
                      X = "vdem_polyarchy", 
                      treat.type = "continuous",
                      Z = c("log_pop", "log_gdp_pc",
                            "log_gdp_pc_sq"),
                      data = data_ova, 
                      FE = c("year"),
                      na.rm = T,
                      estimator = "raw", 
                      vcov.type = "robust", 
                      main = "Marginal Effects", 
                      ylim = c(-15, 15))

## Plot raw
plot(out1_raw)

## Marginal effects plot 
out1 <- interflex(Y = "log_ghg_pc", 
                  D = "log_cc_outs", 
                  X = "vdem_polyarchy", 
                  treat.type = "continuous",
                  Z = c("log_pop", "log_gdp_pc",
                        "log_gdp_pc_sq"),
                  data = data_ova, 
                  FE = c("year"),
                  na.rm = T,
                  estimator = "binning", 
                  vcov.type = "robust", 
                  main = "Marginal Effects", 
                  ylim = c(-15, 15))


pdf("plots/Marginal_interflex.pdf", width = 12)

plot(out1,
     pool = T,
     xlab = "Democracy",
     ylab = "Marginal Effect of Pollution Outsourcing",
     Dlabel = "",
     theme.bw = TRUE, show.grid = FALSE,
     cex.axis = 0.8, cex.lab = 0.8, color = viridis(3)[1], legend.title = "")

dev.off()


## non-linear? --> YES
out1$tests$p.wald
out1$est.bin

```

## Simulate expected values: Model group 1 

```{r expected values 1}

#-------------------------------------------------------------------------------
# Get X for observed value approach
#-------------------------------------------------------------------------------

# make sure I will select the right columns for the year dummies
first_year <- which(colnames(data_ova) == "year_1991") # or 1990?
last_year <- which(colnames(data_ova) == "year_2015")

# Get X
length(coefficients(m3))
X1 <- as.matrix(cbind(1,
                      data_ova$vdem_polyarchy,
                      data_ova$log_pop,
                      data_ova$log_gdp_pc, 
                      data_ova$log_gdp_pc_sq,
                      data_ova[,c(first_year:last_year)]))

X <- na.omit(X1)
dim(X1)

## Get colnames
colnames(X1) <- names(coefficients(m3))


#-------------------------------------------------------------------------------
# Install simulation github Rittmann et al. (2023)
#-------------------------------------------------------------------------------
install_github("mneunhoe/simloglm")
library (simloglm)

## Function to sample from inverse gamma distribution
rinvgamma <- function(n, shape, rate = 1, scale = 1/rate){
  if(missing(rate) && !missing(scale))
    rate <- 1/scale
  1/stats::rgamma(n, shape, rate)
}


# Set up informal posterior of coefficients
nsim <- 1000 # number of draws

beta_hat1 <- c()

for(i in 1:length(coefficients(m3))){
  beta_hat1[i] <- c(coefficients(m3)[[i]])
}

## Get colnames
names(beta_hat1) <- names(coefficients(m3))

sigma_hat1 <- summary(m3)$sigma
X_prime_X1 <- as.matrix(vcov(m3)) / summary(m3)$sigma^2 ## equivalent to vcov$unscaled

# First sigma^2
set.seed(199610)
sigma2_tilde1 <- rinvgamma(nsim,
                           shape = df.residual(m3)/2,
                           rate = (sigma_hat1^2*df.residual(m3))/2)

# Now the betas
beta_tilde1 <- matrix(NA,
                      nrow = nsim,
                      ncol = length(beta_hat1))

for(sim in 1:nsim){
  beta_tilde1[sim, ] <-
    MASS::mvrnorm(1, beta_hat1, X_prime_X1 * sigma2_tilde1[sim])
}



#-------------------------------------------------------------------------------
# Set scenarios: over range of democracy 
#-------------------------------------------------------------------------------

#-------------------------------------------------------------------------------
# Determine "reasonable" variation of democracy variable (within)

# and the respective values (min and max > used for setting the scenario) 
min_dem <- out1$est.bin$`log_cc_outs=1.843 (50%)`[1,1]  
max_dem <- out1$est.bin$`log_cc_outs=1.843 (50%)`[3,1]

# Within range
range_dem_w <- as.vector(seq(min_dem, max_dem, length.out = 30))


#-------------------------------------------------------------------------------
# Create CASES
#-------------------------------------------------------------------------------

# Create empty matrix to store the scenarios
cases1w <- array(NA, 
                 c(dim(X1), length(range_dem_w)))

# Copy in our X
cases1w[,,] <- X1 # because OVA not Average case!

# Select: Democracy over range
select <- which(colnames(X1) == "vdem_polyarchy")

for(i in 1:length(range_dem_w)){
  cases1w[ ,select, i] <- range_dem_w[i]
}

head(cases1w)
dim(cases1w) 
# check dimensions 

# Calculate linear predictor on log scale & retransform
E_Y_c_dem_1w <- matrix(NA, nrow = nsim, ncol = length(range_dem_w)) # empty matrix for storage

for(i in 1:length(range_dem_w)){             # 30 rounds (for range of dem variable)
   ev <- beta_tilde1 %*% t(cases1w[,,i])     # calculate linear predictor on log scale
   ev_plus_gamma <- ev + 1/2*sigma2_tilde1   # add draws of 1/2*sigma2_tilde
   ev_transf <- exp(ev_plus_gamma)           # transform
   ev_transf_m <- ev_transf #- 1             # E(y) 
   tmp_val <- apply(ev_transf_m, 1, mean)    # now average results
   E_Y_c_dem_1w[,i] <- tmp_val               # store in val object
}

# Summarize to get CIs
CI_E_Y_c_dem_1w <- apply(E_Y_c_dem_1w, 2, quantile, c(0.025, 0.975))

# Now get the point estimates 
E_Y_c_hat_dem_1w <- matrix(NA, nrow = length(range_dem_w), ncol = 1)

for(i in 1:length(range_dem_w)){                       # 30 rounds (for range of dem variable)
  ev_point <- beta_hat1 %*% t(cases1w[,,i])            # use beta_hat (not simulated)
  ev_point_plus_gamma <- ev_point + 1/2*sigma_hat1^2   # use sigma_hat (not simulated)
  ev_point_transf <- exp(ev_point_plus_gamma)          # transform
  ev_point_transf_m <- ev_point_transf #- 1            # E(y) 
  tmp_val_point <- apply(ev_point_transf_m, 1, mean)   # now average results
  E_Y_c_hat_dem_1w[i,] <- tmp_val_point                # store in val object
}


#-------------------------------------------------------------------------------
# Plot: Expected values of pollution outsourcing (on original scale)
#-------------------------------------------------------------------------------

pdf("plots/Expected value_m1.pdf") 

par(mar = c(5.1, 4.7, 4.1, 2.1)) # c(bottom, left, top, right))

plot(range_dem_w,
     E_Y_c_hat_dem_1w,
     type = "n",
     ylim = c(40, 80),
     xlim = c(min_dem, max_dem),
     ylab = expression("Pollution Outsourcing [Gg]"),
     xlab = "Democracy",
     bty = "n",
     main = NULL,
     cex.lab = 1.3)

segments(x0 = range_dem_w, x1 = range_dem_w,
         y1 = CI_E_Y_c_dem_1w[2,], y0 = CI_E_Y_c_dem_1w[1,],
         col = viridis(3, 0.25)[1],
         lwd = 4, lend = 1)

points(range_dem_w, E_Y_c_hat_dem_1w, col = viridis(3, 0.8)[1], pch = 20,
       cex = 1.5)


# Add a "histogram" of actual X1-values.
axis(1,
     at = data_ova$vdem_polyarchy,
     col.ticks = "gray30",
     labels = FALSE,
     tck = 0.02)

dev.off()


#-------------------------------------------------------------------------------
# First difference (WITHIN)
#-------------------------------------------------------------------------------

## First difference: Democracy high - low
FD_dem_hat_1w <- E_Y_c_hat_dem_1w[30,] - E_Y_c_hat_dem_1w[1,]  ## max - min
FD_dem_1w <- E_Y_c_dem_1w[,30] - E_Y_c_dem_1w[,1] 
CI_FD_dem_1w <- quantile(FD_dem_1w, c(0.025, 0.975))

#-------------------------------------------------------------------------------
## How "big" is the difference compared to variation in the dataset?
#-------------------------------------------------------------------------------
sd_outs <- aggregate(data_ova$cf_cc_pop_mean_outs,
                     by = list(data_ova$cname),
                     FUN = sd)

mean_within_country_sd <- mean(sd_outs[,2], na.rm = T)
mean_between_country_sd <- sd(data_ova$mean_cc_outs, na.rm = T)
share_FD_var_w <- FD_dem_hat_1w / mean_within_country_sd

```

## Simulate expected values and first differences: Model group 2 

```{r expected values 2}

#-------------------------------------------------------------------------------
# Get X for observed value approach
#-------------------------------------------------------------------------------

# make sure I will select the right columns for the year dummies
first_year <- which(colnames(data_ova) == "year_1991") # or 1990?
last_year <- which(colnames(data_ova) == "year_2015")

# Get X
coefficients(m8)
X <- as.matrix(cbind(1,
                     data_ova$log_cc_outs,
                     data_ova$vdem_polyarchy,
                     data_ova$log_pop,
                     data_ova$log_gdp_pc, 
                     data_ova$log_gdp_pc_sq,
                     data_ova[,c(first_year:last_year)],
                     data_ova$log_cc_outs * data_ova$vdem_polyarchy))

X <- na.omit(X)
dim(X)

## Get colnames
colnames(X) <- names(coefficients(m8))

#-------------------------------------------------------------------------------
# Start with set-up for retransformation
#-------------------------------------------------------------------------------
# Set up informal posterior of coefficients
nsim <- 1000 # number of draws

beta_hat <- c()

for(i in 1:length(coefficients(m8))){
  beta_hat[i] <- c(coefficients(m8)[[i]])
}

## Get colnames
names(beta_hat) <- names(coefficients(m8))

sigma_hat <- summary(m8)$sigma
X_prime_X <- as.matrix(vcov(m8)) / summary(m8)$sigma^2 ## equivalent to vcov$unscaled

# First sigma^2
set.seed(199610)
sigma2_tilde <- rinvgamma(nsim,
                          shape = df.residual(m8)/2,
                          rate = (sigma_hat^2*df.residual(m8))/2)

# Now the betas
beta_tilde <- matrix(NA,
                     nrow = nsim,
                     ncol = length(beta_hat))

for(sim in 1:nsim){
  beta_tilde[sim, ] <-
    MASS::mvrnorm(1, beta_hat, X_prime_X * sigma2_tilde[sim])
}


#-------------------------------------------------------------------------------
# Set scenarios
#-------------------------------------------------------------------------------

#-------------------------------------------------------------------------------
# Determine "reasonable" variation of outsourcing
range_outsource_w <- aggregate(data_ova$log_cc_outs,
                               by = list(data_ova$cname),
                               FUN = mean)


min_outsource_w <- quantile(range_outsource_w[,2], 0.20)
max_outsource_w <- quantile(range_outsource_w[,2], 0.80)

min_outsource_country <- data_ova$cname[which(data_ova$log_cc_outs %like% min_dem)]
max_outsource_country <- data_ova$cname[which(data_ova$log_cc_outs %like% max_dem)]

#-------------------------------------------------------------------------------
# Determine "reasonable" variation of dem (values from binning)
# see above (Model 1)

min_dem_country <- data_ova$cname[which(data_ova$vdem_polyarchy %like% min_dem)]
max_dem_country <- data_ova$cname[which(data_ova$vdem_polyarchy %like% max_dem)]


#-------------------------------------------------------------------------------
## Create empty matrix to store the scenarios
cases_w <- array(NA, 
                c(dim(X), 4))

## Copy in our X
cases_w[,,] <- X

## Add names
colnames(cases_w) <- names(beta_hat)

head(cases_w)

## Case 1: min dem & min outsource
cases_w[ ,"vdem_polyarchy", 1] <- min_dem
cases_w[ ,"log_cc_outs", 1] <- min_outsource_w
cases_w[ ,"log_cc_outs:vdem_polyarchy", 1] <- min_dem* min_outsource_w

## Case 2: min dem & max outsource
cases_w[ ,"vdem_polyarchy", 2] <- min_dem
cases_w[ ,"log_cc_outs", 2] <- max_outsource_w
cases_w[ ,"log_cc_outs:vdem_polyarchy", 2] <- min_dem* max_outsource_w

## Case 3: max dem & min outsource
cases_w[ ,"vdem_polyarchy", 3] <- max_dem
cases_w[ ,"log_cc_outs", 3] <- min_outsource_w
cases_w[ ,"log_cc_outs:vdem_polyarchy", 3] <- max_dem*min_outsource_w

## Case 4: max dem & max outsource
cases_w[ ,"vdem_polyarchy", 4] <- max_dem
cases_w[ ,"log_cc_outs", 4] <- max_outsource_w
cases_w[ ,"log_cc_outs:vdem_polyarchy", 4] <- max_dem*max_outsource_w

## Alternatively
# cases_w[ ,"vdem_polyarchy", 1] <- min_dem
# cases_w[ ,"log_cc_outs", 1] <- mean(data_ova$log_cc_outs, na.rm = T) # min_outsource_w
# cases_w[ ,"log_cc_outs:vdem_polyarchy", 1] <- min_dem*mean(data_ova$log_cc_outs, na.rm = T) # min_outsource_w
# 
# ## Case 2: min dem & max outsource
# cases_w[ ,"vdem_polyarchy", 2] <- max_dem
# cases_w[ ,"log_cc_outs", 2] <- mean(data_ova$log_cc_outs, na.rm = T) # max_outsource_w
# cases_w[ ,"log_cc_outs:vdem_polyarchy", 2] <- max_dem*mean(data_ova$log_cc_outs, na.rm = T) # max_outsource_w


#-------------------------------------------------------------------------------
## Calculate linear predictor on log scale & retransform
#-------------------------------------------------------------------------------
E_Y_c_w <- matrix(NA, nrow = nsim, ncol = 4)  # empty matrix for storage

for(i in 1:4){                              # four rounds (for scenarios)
  ev <- beta_tilde %*% t(cases_w[,,i])      # calculate linear predictor on log scale
  ev_plus_gamma <- ev + 1/2*sigma2_tilde    # add draws of 1/2*sigma2_tilde
  ev_transf <- exp(ev_plus_gamma)           # transform
  ev_transf_m <- ev_transf - 1              # E(y) - 1
  tmp_val <- apply(ev_transf_m, 1, mean)    # now average results
  E_Y_c_w[,i] <- tmp_val                    # store in val object
}

## Summarize to get CIs
CI_E_Y_c_w <- apply(E_Y_c_w, 2, quantile, c(0.025, 0.5, 0.975))

## Now get the point estimates 
E_Y_c_hat_w <- matrix(NA, nrow = 4, ncol = 1)

for(i in 1:4){                                       # four rounds (for scenarios)
  ev_point <- beta_hat %*% t(cases_w[,,i])           # use beta_hat (not simulated)
  ev_point_plus_gamma <- ev_point + 1/2*sigma_hat^2  # use sigma_hat (not simulated)
  ev_point_transf <- exp(ev_point_plus_gamma)        # transform
  ev_point_transf_m <- ev_point_transf - 1           # E(y) - 1
  tmp_val_point <- apply(ev_point_transf_m, 1, mean) # now average results
  E_Y_c_hat_w[i,] <- tmp_val_point                   # store
}


#-------------------------------------------------------------------------------
# First differences
#-------------------------------------------------------------------------------

## First difference: Democracy low -> Outsource max - min
FD_dem_low_hat_w <- E_Y_c_hat_w[2,] - E_Y_c_hat_w[1,]  ## max - min
FD_dem_low_w <- E_Y_c_w[,2] - E_Y_c_w[,1] 
CI_FD_dem_low_w <- quantile(FD_dem_low_w, c(0.025, 0.975))

## First difference: Democracy high -> Outsource max - min
FD_dem_high_hat_w <- E_Y_c_hat_w[4,] - E_Y_c_hat_w[3,]  ## max - min
FD_dem_high_w <- E_Y_c_w[,4] - E_Y_c_w[,3] 
CI_FD_dem_high_w <- quantile(FD_dem_high_w, c(0.025, 0.975))

## First difference of first difference
FD_FD_hat_w <- FD_dem_high_hat_w - FD_dem_low_hat_w
FD_FD_w <- FD_dem_high_w - FD_dem_low_w
CI_FD_FD_w <- quantile(FD_FD_w, c(0.025, 0.975))


#-------------------------------------------------------------------------------
## Plot First differences
#-------------------------------------------------------------------------------
pdf("plots/FD_interaction.pdf")

plot(y = 1,
     x = FD_dem_low_hat_w,
     col = viridis(3)[1],
     ylim = c(0,3),
     xlim = c(-3,0.5),
     xlab = "GHG emissions [metric tons per capita]",
     pch = 19,
     main = NULL, 
     bty = "n",
     ylab = "",
     yaxt = "n",
     cex = 3,
     cex.lab = 1.1)

segments(y0 = 1, x0 = CI_FD_dem_low_w[1],
         y1 = 1, x1 = CI_FD_dem_low_w[2],
         col = viridis(3)[1],
         lwd = 12, cex = 1.5, lend = 1)

segments(y0 = 2, x0 = CI_FD_dem_high_w[1],
         y1 = 2, x1 = CI_FD_dem_high_w[2],
         col = viridis(3)[1],
         lwd = 12, cex = 1.5, lend = 1)

points(y = 2,
       x = FD_dem_high_hat_w,
       col = viridis(3)[1],
       xlab = "",
       pch = 19,
       main = NULL, 
       bty = "n",
       ylab = "",
       yaxt = "n",
       cex = 3,
       cex.lab = 1.1)

segments(x0 = 0, y0 = 0,
         x1 = 0, y1 = 3,
         lty = "dashed", lwd = 2)

text(x = FD_dem_low_hat_w,
     y = 0.8,
     labels = c("Less democratic"),
     cex = 1.1)

text(x = FD_dem_low_hat_w,
     y = 0.57,
     labels = c("Outsourcing (max - min)"),
     cex = 0.9)

text(x = FD_dem_high_hat_w,
     y = 1.8,
     labels = c("More democratic"),
     cex = 1.1)

text(x = FD_dem_high_hat_w,
     y = 1.57,
     labels = c("Outsourcing (max - min)"),
     cex = 0.9)

dev.off()

## First difference of first difference
pdf("plots/FD_FD.pdf")

plot(y = 1.5,
     x = FD_FD_hat_w,
     col = viridis(3)[1],
     ylim = c(0,3),
     xlim = c(-2,0.5),
     xlab = "GHG emissions [metric tons per capita]",
     pch = 19,
     main = NULL, 
     bty = "n",
     ylab = "",
     yaxt = "n",
     cex = 3,
     cex.lab = 1.1)

segments(y0 = 1.5, x0 = CI_FD_FD_w[1],
         y1 = 1.5, x1 = CI_FD_FD_w[2],
         col = viridis(3)[1],
         lwd = 12, cex = 1.5, lend = 1)

segments(x0 = 0, y0 = 0,
         x1 = 0, y1 = 3,
         lty = "dashed", lwd = 2)

text(x = FD_FD_hat_w,
     y = 1.26,
     labels = c("FD of FD"),
     cex = 1.1)

text(x = FD_FD_hat_w,
     y = 1.05,
     labels = c("Democracy (more - less)"),
     cex = 0.9)

dev.off()


```



# Robustness

## Replacing DV with PM2.5

```{r replace DV pm25}

#-------------------------------------------------------------------------------
# Model group 2 
#-------------------------------------------------------------------------------
m8_pm25 <- lm(log_pm25_pop ~ log_cc_outs + vdem_polyarchy + log_cc_outs*vdem_polyarchy +
           log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), data = data_ova)

stargazer(m8, m8_pm25, type = "text", omit = c("ccode", "year"))

```

## Replacing DV with carbon footprint

```{r replace DV carbon footprint}

#-------------------------------------------------------------------------------
# Model group 2 
#-------------------------------------------------------------------------------
m8_cf <- lm(ef_carb ~ log_cc_outs + vdem_polyarchy + log_cc_outs*vdem_polyarchy +
           log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), data = data_ova)

stargazer(m8, m8_cf, type = "text", omit = c("ccode", "year"))


#-------------------------------------------------------------------------------
# Output
#-------------------------------------------------------------------------------
texreg(list(m8, m8_pm25, m8_cf),
       stars = c(0.01, 0.05, 0.1),
      # file = "texreg2.doc",
       caption = "Alternative Dependent Variables",
       custom.model.names = c("Model 7", "Model A1-PM2.5", "Model A2-Carbon Footprint"),
       label = "tab:table3",
       caption.above = T,
       fontsize = "scriptsize",
       custom.coef.map = list("log_cc_outs" = "Pollution Outsourcing",
                              "vdem_polyarchy" = "Democracy",
                              "log_cc_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "log_pop" = "Population",
                              "log_gdp_pc" = "GDP per capita",
                              "log_gdp_pc_sq" = "GDP per capita$^2$",
                              "(Intercept)" = "Constant"),
        custom.gof.rows = list("Controls" = c("\\ding{51}", "\\ding{51}", "\\ding{51}"),
                               "Country-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}"),
                               "Year-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}")))

```

## Different outsourcing variables

```{r diff outsourcing}

#-------------------------------------------------------------------------------
# Model group 2 
#-------------------------------------------------------------------------------
m8_bw <- lm(log_ghg_pc ~ log_bw_outs + vdem_polyarchy + 
                   log_bw_outs*vdem_polyarchy +
                   log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), 
                 data = data_ova)

m8_en <- lm(log_ghg_pc ~ log_en_outs + vdem_polyarchy + 
                   log_en_outs*vdem_polyarchy +
                   log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), 
                 data = data_ova)

m8_lu <- lm(log_ghg_pc ~ log_lu_outs + vdem_polyarchy + 
                   log_lu_outs*vdem_polyarchy +
                   log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), 
                 data = data_ova)

m8_mf <- lm(log_ghg_pc ~ log_mf_outs + vdem_polyarchy + 
                   log_mf_outs*vdem_polyarchy +
                   log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), 
                 data = data_ova)

stargazer(m8, m8_bw, m8_en, m8_lu, m8_mf, type = "text", omit = c("ccode", "year"))


#-------------------------------------------------------------------------------
# Output
#-------------------------------------------------------------------------------
texreg(list(m8, m8_bw, m8_en, m8_lu, m8_mf),
       stars = c(0.01, 0.05, 0.1),
      # file = "texreg2.doc",
       caption = "Alternative Outsourcing Variables",
       custom.model.names = c("Model 7", "Model A3-bluewater", "Model A4-energy", "Model A5-landuse", "Model A6-material"),
       label = "tab:table4",
       caption.above = T,
       fontsize = "scriptsize",
       custom.coef.map = list("log_cc_outs" = "Pollution Outsourcing",
                              "log_bw_outs" = "Pollution Outsourcing",
                              "log_en_outs" = "Pollution Outsourcing",
                              "log_lu_outs" = "Pollution Outsourcing",
                              "log_mf_outs" = "Pollution Outsourcing",
                              "vdem_polyarchy" = "Democracy",
                              "log_cc_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "log_bw_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "log_en_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "log_lu_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "log_mf_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "log_pop" = "Population",
                              "log_gdp_pc" = "GDP per capita",
                              "log_gdp_pc_sq" = "GDP per capita$^2$",
                              "(Intercept)" = "Constant"),
        custom.gof.rows = list("Controls" = c("\\ding{51}", "\\ding{51}", "\\ding{51}","\\ding{51}", "\\ding{51}"),
                               "Country-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}"),
                               "Year-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}")))

```

## Alternative operationalization outsourcing: Total sum of pollution outsourced

```{r total sum}

#-------------------------------------------------------------------------------
# Model group 1
#-------------------------------------------------------------------------------
m1_sum <- lm(log_cc_sum_outs ~ vdem_polyarchy + as.factor(year), data = data_ova)
m2_sum <- lm(log_cc_sum_outs ~ log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year),data = data_ova)
m3_sum <- lm(log_cc_sum_outs ~ vdem_polyarchy + log_pop + log_gdp_pc + log_gdp_pc_sq +  as.factor(year), data = data_ova)

stargazer(m1_sum, m2_sum, m3_sum, type = "text", omit = c("ccode", "year"))


#-------------------------------------------------------------------------------
## Output
#-------------------------------------------------------------------------------
texreg(list(m1_sum, m2_sum, m3_sum),
       stars = c(0.01, 0.05, 0.1),
       #file = "texreg1.doc",
       caption = "Total Sum of Pollution Outsourced - Analysis 1",
       custom.model.names = c("Model A7", "Model A8", "Model A9"),
       label = "tab:table5",
       caption.above = T,
       fontsize = "scriptsize",
       custom.coef.map = list("vdem_polyarchy" = "Democracy",
                              "log_pop" = "Population",
                              "log_gdp_pc" = "GDP per capita",
                              "log_gdp_pc_sq" = "GDP per capita$^2$", 
                              "(Intercept)" = "Constant"),
        custom.gof.rows = list("Controls" = c("\\xmark", "\\ding{51}", "\\ding{51}"),
                               "Country-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}"),
                               "Year-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}")))


#-------------------------------------------------------------------------------
# Model group 2
#-------------------------------------------------------------------------------
m5_sum <- lm(log_ghg_pc ~ log_cc_sum_outs + vdem_polyarchy + as.factor(year), data = data_ova)

m6_sum <- lm(log_ghg_pc ~ log_cc_sum_outs + vdem_polyarchy + 
              log_cc_sum_outs*vdem_polyarchy +
              as.factor(year), data = data_ova)

m7_sum <- lm(log_ghg_pc ~ log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), data = data_ova)

m8_sum <- lm(log_ghg_pc ~ log_cc_sum_outs + vdem_polyarchy + 
              log_cc_sum_outs*vdem_polyarchy +
              log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), data = data_ova)

stargazer(m5_sum, m6_sum, m7_sum, m8_sum, type = "text", omit = c("ccode", "year"))


#-------------------------------------------------------------------------------
# Output
#-------------------------------------------------------------------------------
texreg(list(m5_sum, m6_sum, m7_sum, m8_sum),
       stars = c(0.01, 0.05, 0.1),
      # file = "texreg2.doc",
       caption = "Total Sum of Pollution Outsourced - Analysis 2",
       custom.model.names = c("Model A10", "Model A11", "Model A12", "Model A13"),
       label = "tab:table6",
       caption.above = T,
       fontsize = "scriptsize",
       custom.coef.map = list("log_cc_sum_outs" = "Pollution Outsourcing",
                              "vdem_polyarchy" = "Democracy",
                              "log_cc_sum_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "log_pop" = "Population",
                              "log_gdp_pc" = "GDP per capita",
                              "log_gdp_pc_sq" = "GDP per capita$^2$",
                              "(Intercept)" = "Constant"),
        custom.gof.rows = list("Controls" = c("\\xmark", "\\xmark", "\\ding{51}", "\\ding{51}"),
                               "Country-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}"),
                               "Year-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}")))


```

## Alternative operationalization for democracy

```{r diff  dem}

#-------------------------------------------------------------------------------
# Model group 2 
#-------------------------------------------------------------------------------
m8_polity <- lm(log_ghg_pc ~ log_cc_outs + p_polity2 + 
                     log_cc_outs*p_polity2 +
                     log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year), data = data_ova)

stargazer(m8, m8_polity, type = "text", omit = c("ccode", "year"))


#-------------------------------------------------------------------------------
# Output
#-------------------------------------------------------------------------------
texreg(list(m8, m8_polity),
       stars = c(0.01, 0.05, 0.1),
      # file = "texreg2.doc",
       digits = 3,
       caption = "Alternative Operationalization for Democracy",
       custom.model.names = c("Model 7-Vdem", "Model A14-Polity"),
       label = "tab:table6",
       caption.above = T,
       fontsize = "scriptsize",
       custom.coef.map = list("log_cc_outs" = "Pollution Outsourcing",
                              "vdem_polyarchy" = "Democracy",
                              "p_polity2" = "Democracy",
                              "log_cc_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "log_cc_outs:p_polity2" = "Pollution Outsourcing x Democracy",
                              "log_pop" = "Population",
                              "log_gdp_pc" = "GDP per capita",
                              "log_gdp_pc_sq" = "GDP per capita$^2$",
                              "(Intercept)" = "Constant"),
        custom.gof.rows = list("Controls" = c("\\ding{51}", "\\ding{51}"),
                               "Country-FE" = c("\\ding{51}", "\\ding{51}"),
                               "Year-FE" = c("\\ding{51}", "\\ding{51}")))

```

## Additional controls: Trade, political globaliz. & env. treaties, GDP

```{r additional controls}

#-------------------------------------------------------------------------------
# Model group 2 
#-------------------------------------------------------------------------------
m8_ac1 <- lm(log_ghg_pc ~ vdem_polyarchy + log_cc_outs*vdem_polyarchy +
               log_pop + log_gdp_pc + log_gdp_pc_sq + wdi_trade + as.factor(year), 
             data = data_ova)

m8_ac2 <- lm(log_ghg_pc ~ vdem_polyarchy + log_cc_outs*vdem_polyarchy +
               log_pop + log_gdp_pc + log_gdp_pc_sq + env_treaties + as.factor(year), 
             data = data_ova)

m8_ac3 <- lm(log_ghg_pc ~ vdem_polyarchy + log_cc_outs*vdem_polyarchy +
               log_pop + log_gdp_pc + log_gdp_pc_sq + dr_pg + as.factor(year), 
             data = data_ova)

m8_ac4 <- lm(log_ghg_pc ~ vdem_polyarchy + log_cc_outs*vdem_polyarchy +
               log_pop + log_gdp_pc + log_gdp_pc_sq + log_gdp + as.factor(year), 
             data = data_ova)

m8_ac_all <- lm(log_ghg_pc ~ vdem_polyarchy + log_cc_outs*vdem_polyarchy +
                 log_pop + log_gdp_pc + log_gdp_pc_sq + 
                 wdi_trade + env_treaties + dr_pg + log_gdp + as.factor(year), 
                data = data_ova)


stargazer(m8, m8_ac1, m8_ac2, m8_ac3, m8_ac4, m8_ac_all, type = "text", omit = c("ccode", "year"))


texreg(list(m8, m8_ac1, m8_ac2, m8_ac3, m8_ac4, m8_ac_all),
       stars = c(0.01, 0.05, 0.1),
      # file = "texreg2.doc",
       caption = "Additional Control Variables",
       custom.model.names = c("Model 7", "Model A15", "Model A16", "Model A17", "Model A18", "Model A19"),
       label = "tab:table7",
       caption.above = T,
       fontsize = "scriptsize",
       custom.coef.map = list("log_cc_outs" = "Pollution Outsourcing",
                              "vdem_polyarchy" = "Democracy",
                              "log_cc_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "vdem_polyarchy:log_cc_outs" = "Pollution Outsourcing x Democracy",
                              "log_pop" = "Population",
                              "log_gdp_pc" = "GDP per capita",
                              "log_gdp_pc_sq" = "GDP per capita$^2$",
                              "wdi_trade" = "Trade Openness",
                              "env_treaties" = "Environmental Treaties",
                              "dr_pg" = "Political Globalization",
                              "log_gdp" = "GDP",
                              "(Intercept)" = "Constant"),
        custom.gof.rows = list("Controls" = c("\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}"),
                               "Country-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}"),
                               "Year-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}", "\\ding{51}")))


```

## Drop high-income states

```{r drop high-income}

#-------------------------------------------------------------------------------
# Model group 2 
#-------------------------------------------------------------------------------
m8_low_income <- lm(log_ghg_pc ~ log_cc_outs + vdem_polyarchy + log_cc_outs*vdem_polyarchy +
                         log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year),
                       data = data_ova[data_ova$log_gdp_pc < 10.1,])

stargazer(m8, m8_low_income, type = "text", omit = c("ccode", "year"))


#-------------------------------------------------------------------------------
# Output
#-------------------------------------------------------------------------------
texreg(list(m8, m8_low_income),
       stars = c(0.01, 0.05, 0.1),
      # file = "texreg2.doc",
       caption = "Exclusion of the Richest States",
       custom.model.names = c("Model 7", "Model A20"),
       label = "tab:table9",
       caption.above = T,
       fontsize = "scriptsize",
       custom.coef.map = list("log_cc_outs" = "Pollution Outsourcing",
                              "vdem_polyarchy" = "Democracy",
                              "log_cc_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "log_pop" = "Population",
                              "log_gdp_pc" = "GDP per capita",
                              "log_gdp_pc_sq" = "GDP per capita$^2$",
                              "(Intercept)" = "Constant"),
        custom.gof.rows = list("Controls" = c("\\ding{51}", "\\ding{51}"),
                               "Country-FE" = c("\\ding{51}", "\\ding{51}"),
                               "Year-FE" = c("\\ding{51}", "\\ding{51}")))
```

## RE and TWFE 

```{r RE-TWFE effects}

#-------------------------------------------------------------------------------
# Model group 1 
#-------------------------------------------------------------------------------
## Set up panel data
panel_data <- pdata.frame(data_ova, index = c("ccode", "year"))

m3_cf <- lmer(log_cc_outs ~ vdem_polyarchy + log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year) + (1|ccode), data = data_ova)
m3_twfe <- lm(log_cc_outs ~ vdem_polyarchy + log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(ccode) + as.factor(year), data = data_ova)

stargazer(m3, m3_cf, m3_twfe, type = "text", omit = c("ccode", "year"))

texreg(list(m3, m3_cf, m3_twfe),
       stars = c(0.01, 0.05, 0.1),
       #file = "texreg1.doc",
       custom.header = list("Pollution Outsourcing" = 1:3),
       caption = "Alternative Model Specification -- First-Stage Analysis",
       custom.model.names = c("Model 1", "Model 14", "Model 15"),
       label = "tab:table10",
       caption.above = T,
       fontsize = "scriptsize",
       custom.coef.map = list("vdem_polyarchy" = "Democracy",
                              "log_pop" = "Population",
                              "log_gdp_pc" = "GDP per capita",
                              "log_gdp_pc_sq" = "GDP per capita$^2$", 
                              "(Intercept)" = "Constant"),
        custom.gof.rows = list("Controls" = c("\\xmark", "\\ding{51}", "\\ding{51}"),
                               "RE" = c("\\xmark", "\\ding{51}", "\\xmark"),
                               "Year-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}"),
                               "Country-FE" = c("\\xmark", "\\xmark", "\\ding{51}")))

#-------------------------------------------------------------------------------
# Model group 2 
#-------------------------------------------------------------------------------
m8_cf <- lmer(log_ghg_pc ~ log_cc_outs + vdem_polyarchy + log_cc_outs*vdem_polyarchy +
             log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year) + (1|ccode),
             data = data_ova)

m8_twfe <- lm(log_ghg_pc ~ log_cc_outs + vdem_polyarchy + log_cc_outs*vdem_polyarchy +
             log_pop + log_gdp_pc + log_gdp_pc_sq + as.factor(year) + as.factor(ccode),
             data = data_ova)

stargazer(m8, m8_cf, m8_twfe, type = "text", omit = c("ccode", "year"))


texreg(list(m8, m8_cf, m8_twfe),
       stars = c(0.01, 0.05, 0.1),
      # file = "texreg2.doc",
       caption = "Alternative Model Specification -- Second-Stage Analysis",
       custom.model.names = c("Model 2", "Model 16", "Model 17"),
       label = "tab:table11",
       caption.above = T,
       fontsize = "scriptsize",
       custom.coef.map = list("log_cc_outs" = "Pollution Outsourcing",
                              "vdem_polyarchy" = "Democracy",
                              "log_cc_outs:vdem_polyarchy" = "Pollution Outsourcing x Democracy",
                              "log_pop" = "Population",
                              "log_gdp_pc" = "GDP per capita",
                              "log_gdp_pc_sq" = "GDP per capita$^2$",
                              "(Intercept)" = "Constant"),
        custom.gof.rows = list("Controls" = c("\\xmark", "\\ding{51}", "\\ding{51}"),
                               "RE" = c("\\xmark", "\\ding{51}", "\\xmark"),
                               "Year-FE" = c("\\ding{51}", "\\ding{51}", "\\ding{51}"),
                               "Country-FE" = c("\\xmark", "\\xmark", "\\ding{51}")))
```
